---
title: "Week 2: Text Data in R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents
https://alexluscombe.ca/post/r-pdftools/
https://alexluscombe.ca/blog/parsing-your-.pdfs-in-r/

Basic workflow for text analysis
Obtain your text sources
Text data can come from lots of areas:

Web sites
Twitter
Databases
PDF documents
Digital scans of printed materials
The easier to convert your text data into digitally stored text, the cleaner your results and fewer transcription errors.

Extract documents and move into a corpus
A text corpus is a large and structured set of texts. It typically stores the text as a raw character string with meta data and details stored with the text.

Transformation
Examples of typical transformations include:

Tagging segments of speech for part-of-speech (nouns, verbs, adjectives, etc.) or entity recognition (person, place, company, etc.)
Standard text processing - we want to remove extraneous information from the text and standardize it into a uniform format. This typically involves:
Converting to lower case
Removing punctuation
Removing numbers
Removing stopwords - common parts of speech that are not informative such as a, an, be, of, etc.
Removing domain-specific stopwords
Stemming - reduce words to their word stem
“Fishing”, “fished”, and “fisher” -> “fish”
Extract features
Feature extraction involves converting the text string into some sort of quantifiable measures. The most common approach is the bag-of-words model, whereby each document is represented as a vector which counts the frequency of each term’s appearance in the document. You can combine all the vectors for each document together and you create a term-document matrix:

Each row is a document
Each column is a term
Each cell represents the frequency of the term appearing in the document

Import data/parse pdf
Create tibble
Inspect
Basic frequency analyses


## Including Code

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
